\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-16 europa.tex
citations added to europa text

The Constraint Reasoning Engine (CRE) manages variables, the domains
from which they can take values, and constraints that define
relationships among variables. It also provides an efficient arc
consistency mechanism \cite{mackworth77}. The CRE is designed so that
specialized reasoning algorithms for specific constraints can be easily
and efficiently plugged in. The Plan Database (PDB) manages object types
and objects, which are a mechanism to group variables to more naturally
model the real world in much the same way that object oriented
programming does. Also manages tokens, which are a mechanism to group
variables to represent temporally scoped state. Objects and tokens can
be used to model planning domains in a much more natural and extensible
way that a pure CSP approach can. The Rules Engine (RE) manages token
relationships in a planning model. The language modules (NDDL, ANML, and
other higher level modeling languages) are used to create domain models
and problem instances \comment{point advantages over pure programming
  API approaches, provide snippets}. Finally the API Layer (Fig.
\ref{fig:europa-api}) makes all the services available so that \eu can
be used to build applications.

\comment{Is Fig. \ref{fig:europa-api} necessary?}

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/EUROPA-API.jpg}
\caption{\small EUROPA's Client API}
\label{fig:europa-api}
\vskip+0.1cm
\end{figure}

	% \item Extension Modules bundled with EUROPA: Temporal Network, Resources, NDDL, ANML.
	% 	\begin{enumerate}
	% 		\item Temporal Network
	% 		\item Resources
	% 		\item NDDL
	% 		\item ANML (TODO:maybe it's better to leave out?)
	% 	\end{enumerate}

@@

  predicate Own {
  	Product product;
  }
}

@@

In this model we can see:

\comment{explain variable, object, predicate and action types, including constraints that can be part of them}
\begin{enumerate}
	\item Variable Types: This model uses integer (activity duration, start and end times, etc) and string (Location and Product names, etc)
	\item Object Types:
	\item Predicate Types:
	\item Action Types:
\end{enumerate}

 shows how a specific problem instance would be
specified in NDDL.

@@

\label{eu:model}
\end{verbatim}

\comment{explain variable, object, predicate and constraint instances.
explain goals and facts.}

\begin{enumerate}
	\item Variable Instances:
	\item Object Instances:
	\item Facts:
	\item Goals:
	\item Constraint Instances:
\end{enumerate}

@@

\comment{ add figure}

>>>>

The \textbf{Constraint Reasoning Engine} (CRE) manages domain types, variables and constraints that define
relationships among them. It also provides an efficient arc
consistency mechanism \cite{mackworth77}. The CRE is designed so that
specialized reasoning algorithms for specific constraints can be easily
and efficiently plugged in.

The \textbf{Plan Database} (PDB) manages object and token types. It also maintains the state of partial plans in terms of object, variable and token instances. This constitutes the data foundation on which end user applications and automated planners are built.

The \textbf{Rules Engine} (RE) modularly adds the capability to support domain rules that describe dependencies between tokens,

The \textbf{Solver Module} provides the framework for flaw detection and resolution that is needed to implement search algorithms for planning.

The \textbf {Language Modules}: Describing problem domains and problem instances in terms of objects, variables and domain rules in a programmatic way is cumbersome to the extent of being impractical, that motivated the creation of modeling languages that support those definitions in a much more natural and compact way. NDDL is the main modeling language for \eu and will be described in detail in the Modeling section below. ANML is a language under development that provides a more intuitive syntax \comment{provide ANML citation}.

The \textbf{API Layer}  provides access to services from all the different modules in a programmatic way so that \eu can be easily embedded into specialized applications.

In an effort to mimimize the amount of work that a user needs to perform to solve specific problems, \eu  also provides extension modules that have been found to be useful in many domains: 
\begin{enumerate}
	\item \textit{Temporal Network}: Extensions to the CRE module to reason about temporal constraints 
	\item \textit{Resources}: Extensions to the CRE, PDB and Solver modules to provide out-of-the-box reasoning and search for metric resources.
	\item \textit{Chronological Backtracking Solver}: A general purpose built-in solver to provide the ability to plan out-of-the-box, problems that require challenging search may require specialized solvers to be built as explained in the Search section below.	
\end{enumerate}

@@

  predicate Own {
  	Product product;
  }
}
\end{verbatim}

In the model above we can see how the main elements or a problem domain can be mapped to \eu's representation:

\begin{enumerate}
	\item \textbf{Object Types}: NDDL supports an object-oriented approach, where common data and behavior can be abstracted as a class. In this case, we have the \textit{Product} class represent the products that the Shopping Agent needs, \textit{Location} represents the places where products can be found, \textit{ProductLocation} represents the association arising when a product can be purchased at a location. The Shopping Agent itself is represented by an \textit{Agent} class, which relies on the \textit{AgentLocation} class to keep track of where the agent is at any point in time. NDDL supports a single rooted class hierarchy so that state and behavior can be extended through inheritance. We took advantage of that by making \textit{AgentLocation} inherit from \eu's built-in \textit{Timeline} class which doesn't allow predicates to overlap in time for the same object instance, in this way we can ensure that and agent can only be at one place at a time. 
	\item \textbf{Variable Types and Instances} : All object attributes are represented as variables in this model, for instance, it uses integer variables to represent the built-in temporal parameters for each token (activity duration, start and end times), string variables to represent  \textit{Location} and  \textit{Product} names, and object reference variables to represent the structural relationships between different objects (for instance, each Agent has variable to keep track of its  \textit{AgentLocation}).
	\item \textbf{Predicate Types}: Some classes like \textit{Product}, \textit{Location} and \textit{ProductLocation} are completely static and so don't have any predicate or action types associated with them. The \textit{AgentLocation} class is purely used to keep track of state and so it has \texttt{At} and \texttt{Going} predicate types associated with it. The \textit{Agent} class keeps track of the products it purchases through the \texttt{Own} predicate, having a separate \textit{AgentBag} class with its own predicates would have been an equally valid modeling choice.
	\item \textbf{Action Types}: The \textit{Agent} class is the only one that has behavior associated with it, consequently, it defines action types to represent when the agent is taking action to \texttt{Go} to a \textit{Location}, or to \texttt{Buy} a \textit{Product}. We'll see how the actual behavior for those actions is specified below.
\end{enumerate}

@@

Domain rules can be defined in NDDL in the context of a Predicate or an Action. In the example above we can see the main elements of a rule definition:

\begin{enumerate}
  \item \textbf{Variables}: A Token Type (predicate or action) is part of a class, therefore class attributes (see references to \texttt{object.location} above), Token Type parameters (see references to \texttt{[from, to]}  in \texttt{Agent::Go}, or to \texttt{[duration, product]} in \texttt{Agent::Buy}  and locally declared variables (see \texttt{possibleStores} in \texttt{Agent::Buy}) can all be used in the definition of a Rule. 
  \item \textbf{Constraints}: restrictions on the values that variables can take inside a Rule are expressed through constraints, in the example above only the \texttt{eq} constraint is used, but in general, any constraint available in \eu's library can be used.
 \item \textbf{Subgoals}: In \texttt{Agent::Go}, subgoals are used to specify that the Shopping Agent's location must transition from origin to destination in a temporally consistent way. The \texttt{[meets, equals, metby]} operators are used to specify subgoals (Allen operators are explained in more detail below), along with the temporal relationship each token representing a subgoal has with the the token representing the \texttt{Agent::Go} action. Also, \texttt{[condition, effect]} annotations can be used when defining a subgoal inside an action, \eu doesn't immediately associate any semantics with them, but they can be extremely useful for search modules when creating plans. 
\end{enumerate}

Now, having that we have a specification for the Shopping Agent domain, here is how a particular problem instance could be specified:

@@

\label{eu:model}
%\caption{Specifying a problem instance for the Shopping Agent in NDDL}
\end{verbatim}

A problem instance consists mainly of 
\begin{enumerate}
  \item \textbf{Variables} and \textbf{Objects}: In this case we defined temporal variables that are used to specify the planning horizon (see \texttt{horizonStart} and \texttt{horizonEnd}), and objects are used to specify the locations, products, product-loction associations and the Shopping Agent that we want to plan for.
  \item \textbf{Facts}: These are used to specify the current state of the world and don't need any support. Facts are represented as tokens in \eu's Plan Database. In this case we use facts to specify that the Shipping Agent is initially at home.
  \item \textbf{Goals}:  Goals are represented as tokens in \eu's Plan Database, differently from Facts, Goals trigger inference in \eu which determines whether flaws (unresolved subgoals, overloaded resources, etc., flaws will be covered in detail in the search section below) need to be resolved, if that is the case, search modules can be invoked which will look for a plan where all the flaws are resolved.
  \item \textbf{Constraints}: restrictions on and between actions and goals are specified through constraints, in this case we use temporal constraints to specify when the facts hold and when the goals should be accomplished. As always, all the constraints in \eu's library (built-in, or user defined), can be used to specify these restrictions.
\end{enumerate}

@@

\begin{figure}[!htb]
  \centering
  \subfloat[\small A Simple Temporal Network (STN)]{\label{fig:stn1}\includegraphics[width=0.4\columnwidth]{figs/stn-graph.pdf}}
  \subfloat[\small Resulting distance graph from \ref{fig:stn1}.]{\label{fig:stn2}\includegraphics[width=0.4\columnwidth]{figs/distance-graph.pdf}}
    \caption{\small An illustration of a STN and its corresponding
      distance graph.}
  \label{fig:stn}
\end{figure}

\comment{ add figure. Use Europa wiki figure; or use conor figure from slides}
